Paper 1

### 2018-09-09 paper1.tex
Finished the first question.

\begin{proof}[Correct proof of theorem~\ref{thm:mean-spirited}]
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	% HINTS
	%
	% Use the AM-GM inequality.
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{proof}

>>>>

\begin{proof}[Correct proof of theorem~\ref{thm:mean-spirited}]
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	% HINTS
	%
	% Use the AM-GM inequality.
	%
	From the AM-GM inequality, we know
	\begin{align*}
		\frac{a+b+c}{3} \geq \sqrt[3]{abc}. 
	\end{align*}
	Because we know $abc$ is a positive number, $\sqrt[3]{abc}$ is also positive. So, we can perform the following,
	\begin{align*}
	\frac{(a+b+c)(\sqrt[3]{abc})^2}{3} &\geq abc \\
	\frac{(a+b+c)}{(abc)^{\frac{1}{3}}} &\geq 3 \\
	\frac{(a)^{\frac{2}{3}}}{(bc)^{\frac{1}{3}}} + \frac{(b)^{\frac{2}{3}}}{(ac)^{\frac{1}{3}}} + \frac{(c)^{\frac{2}{3}}}{(ab)^{\frac{1}{3}}}&\geq 3 \\
	\sqrt[3]{\frac{a^2}{bc}}+\sqrt[3]{\frac{b^2}{ac}}+\sqrt[3]{\frac{c^2}{ab}}&\geq 3
	\end{align*}
	We know that all terms are positive in the above inequality, so,
	$$ \frac{a^2}{bc} + \frac{b^2}{ac} + \frac{c^2}{ac} \geq \sqrt[3]{\frac{a^2}{bc}}+\sqrt[3]{\frac{b^2}{ac}}+\sqrt[3]{\frac{c^2}{ab}}\geq3.$$
	This implies that 
	$$ \frac{a^2}{bc} + \frac{b^2}{ac} + \frac{c^2}{ac} \geq 3 .$$
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{proof}
